Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-05-10 WSSSPE4_report/WSSSPE4_paper.tex
starting WSSSPE4 paper, mostly placeholder
starting to shorten removing survey appendix shortening 8.1

\title[]{Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)}

@@

@@

\input{wg_best_practices_sustainability}
\input{wg_alliance}
\input{wg_prototyping}
\input{wg_codemeta}
\input{wg_best_practices_developing}
\input{wg_social}
\input{wg_best_practices_undergrads}
\input{wg_metrics}
\input{wg_access}
\input{wg_soft_eng}
\input{wg_open_research_index}
\input{wg_letters}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Detailed survey results}  \label{sec:survey_details}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{survey_details}

>>>>

\title[]{Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)}

@@

\todo{cite~\cite{WSSSPE4-report}}

@@

\subsection{Verifying best practices \& metrics for sustainable research software}
\label{sec:best-practices-sustainable}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\note{Ray to write this}

Many open source projects for research software document their best practices that
contributed to the sustainability of the software.  Many of these projects also
document software metrics they use to define their research software project's success.
%
This group will take the outputs of the WSSSPE efforts to identify best practices for creation of sustainable software for science/academia, and also the outputs of WSSSPE efforts to identify metrics for sustainable software for science/academia and cross-reference these with current open source research software that successfully uses modern software engineering.  This will allow the group to identify gaps on both sides.  This approach will also allow the group to hypothesize how successful open source projects can be further improved, verify that recommended approaches for software engineering for science/academia are sufficient and valid, and that metrics for software engineering for science/academia are relevant and useful.  The group has a specific objective of getting a good cross-sampling of disparate software including community model codes, community cyberinfrastructure, community analytic tools, etc.

Each group member will volunteer to take on one to two projects, ideally ones in which they are already interested.  This effort will evaluate an initial 5--10 projects.  Once the group documents the workflow by which these evaluations are performed, other people can choose to follow this workflow and contribute their own evaluations of additional software.

To join this group or obtain more information about it, please send an email to the verifying best practices \& metrics for sustainable research software group: <wssspe4-verify-best-practices@googlegroups.com>.

\input{wg_alliance}
\input{wg_prototyping}
\input{wg_codemeta}
\input{wg_best_practices_developing}
\input{wg_social}
\input{wg_best_practices_undergrads}
\input{wg_metrics}
\input{wg_access}
\input{wg_soft_eng}
\input{wg_open_research_index}
\input{wg_letters}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Detailed survey results}  \label{sec:survey_details}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\input{survey_details}
